Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-05 documentation/paper.tex
Added additional information about ICN graphs and updated image

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{icn_grid_search}
    \caption{\label{icn_grid_search} Accuracy of best iterative cluster nucleation training run compared to Acoustic Parameter and original ground truths (100\% accuracy).}
\end{figure}

As seen in Figure \ref{icn_grid_search}, the network learned to replicate Acoustic Parameter very accurately. Interestingly, the examples with Acoustic Parameter values between the neutron and alpha particle ranges were also classified as such by the network.
